Enforced Invariant Confluence

### 2018-05-01 doc/paper/sections/conclusion.tex
Last tweaks!

\textbf{Acknowledgments.}
The authors would like to thank Peter Alvaro, Alvin Cheung, Anthony Tan, and
Cristina Teodoropol for fruitful discussion and feedback.
%
This research is supported in part by DHS Award HSHQDC-16-3-00083, NSF CISE
Expeditions Award CCF-1139158, and gifts from Alibaba, Amazon Web Services, Ant
Financial, CapitalOne, Ericsson, GE, Google, Huawei, Intel, IBM, Microsoft,
Scotiabank, Splunk and VMware.

>>>>

\textbf{Acknowledgments.}
The authors would like to thank Alan Fekete, Peter Alvaro, Alvin Cheung,
Alexandra Meliou, Anthony Tan, and Cristina Teodoropol for fruitful discussion
and feedback.
%
This research is supported in part by DHS Award HSHQDC-16-3-00083, NSF CISE
Expeditions Award CCF-1139158, and gifts from Alibaba, Amazon Web Services, Ant
Financial, CapitalOne, Ericsson, GE, Google, Huawei, Intel, IBM, Microsoft,
Scotiabank, Splunk and VMware.

### 2018-05-01 doc/paper/sections/evaluation.tex
Last tweaks!

Lucy also includes an implementation of the \invariantconfluence{} and
segmented-invariant confluence system models in roughly 3,500 lines of C++.
Users specify objects, transactions, invariants, and segmentations in C++. Lucy
then replicates the objects using segmented \invariantconfluence{}. Clients
send every transaction request to a randomly selected server. When a server
receives a transaction request, it executes \algoref{TxnExecution} to attempt
to execute the transaction locally.  If the transaction requires global
coordination, then the server forwards the transaction request to a
predetermined leader. When the leader receives a transaction request, it
broadcasts a coordination request to the other servers. When a server receives
a coordination request from the leader, it stops processing transactions and
sends the leader its state. When the leader receives the states of all other
servers, it executes the transaction, and then sends its state to the other
servers. When a server receives a new state, it adopts the state, computes its
new active segment, and resumes normal processing. After every 100 transactions
processed, a server sends a merge request to a randomly selected server.

@@

These hypotheses state that segmented \invariantconfluent{} is more performant
than linearizable replication for low-coordination workloads. But by how much?
We also aim to measure the absolute performance and scalability benefits of
segmented \invariantconfluent{} replication and how they vary as we vary the
coordination required by a workload. We perform two controlled microbenchmarks
to confirm our hypotheses and discover the absolute performance benefits. The
workloads themselves are trivial but are not the focus of our experiments. Our objective is to
obtain a controlled measure of throughput and scalability as we vary workload
contention.

>>>>

Lucy also includes an implementation of the \invariantconfluence{} and
segmented \invariantconfluence{} system models in roughly 3,500 lines of C++.
Users specify objects, transactions, invariants, and segmentations in C++. Lucy
then replicates the objects using segmented \invariantconfluence{}. Clients
send every transaction request to a randomly selected server. When a server
receives a transaction request, it executes \algoref{TxnExecution} to attempt
to execute the transaction locally.  If the transaction requires global
coordination, then the server forwards the transaction request to a
predetermined leader. When the leader receives a transaction request, it
broadcasts a coordination request to the other servers. When a server receives
a coordination request from the leader, it stops processing transactions and
sends the leader its state. When the leader receives the states of all other
servers, it executes the transaction, and then sends its state to the other
servers. When a server receives a new state, it adopts the state, computes its
new active segment, and resumes normal processing. After every 100 transactions
processed, a server sends a merge request to a randomly selected server.

@@

These hypotheses state that segmented \invariantconfluent{} replication is more
performant than linearizable replication for low-coordination workloads. But by
how much?  We also aim to measure the absolute performance and scalability
benefits of segmented \invariantconfluent{} replication and how they vary as we
vary the coordination required by a workload. We perform two controlled
microbenchmarks to confirm our hypotheses and discover the absolute performance
benefits. The workloads themselves are trivial but are not the focus of our
experiments. Our objective is to obtain a controlled measure of throughput and
scalability as we vary workload contention.

### 2018-05-01 doc/paper/sections/segmented_invariant_confluence.tex
Added more on performance.
Last tweaks!

If a distributed object is \invariantconfluent{}, then the object can be
replicated without the need for any form of coordination to maintain the
object's invariant. But what if the object is \emph{not} \invariantconfluent{}?
In this section, we present a generalization of \invariantconfluence{} called
\defword{segmented \invariantconfluence{}} that can be used to maintain the
invariants of non-\invariantconfluent{} objects, requiring only a small amount
of coordination.

@@

This system model guarantees that all replicas of a segmented
\invariantconfluent{} object always satisfy the invariant. All servers begin in
the same initial state and with the same active segment. Thus, because $O$ is
\invariantconfluent{} with respect to every segment, servers can execute
transactions within the active segment without any coordination and guarantee
that the invariant is never violated. Any operation that would violate the
assumptions of the \invariantconfluence{} system model (e.g.\ executing a
transaction that's not permitted in the active segment or executing a permitted
transaction that leads to a state outside the active segment) triggers a global
coordination. Globally coordinated transactions are only executed if they
maintain the invariant. Moreover, if a globally coordinated transaction leads
to another segment, the coordination ensures that all servers begin in the same
start state and with the same active replica, reestablishing the assumptions of
the \invariantconfluence{} system model.

>>>>

If a distributed object is \invariantconfluent{}, then the object can be
replicated without the need for any form of coordination to maintain the
object's invariant. But what if the object is \emph{not} \invariantconfluent{}?
In this section, we present a generalization of \invariantconfluence{} called
\defword{segmented \invariantconfluence{}} that can be used to maintain the
invariants of non-\invariantconfluent{} objects, requiring only a small amount
of coordination. In \secref{Evaluation}, we see that replicating a
non-\invariantconfluent{} object with segmented \invariantconfluence{} can
achieve between 100x and 10x more throughput than linearizable replication for
certain workloads.

@@

This system model guarantees that all replicas of a segmented
\invariantconfluent{} object always satisfy the invariant. All servers begin in
the same initial state and with the same active segment. Thus, because $O$ is
\invariantconfluent{} with respect to every segment, servers can execute
transactions within the active segment without any coordination and guarantee
that the invariant is never violated. Any operation that would violate the
assumptions of the \invariantconfluence{} system model (e.g.\ executing a
transaction that's not permitted in the active segment or executing a permitted
transaction that leads to a state outside the active segment) triggers a global
coordination. Globally coordinated transactions are only executed if they
maintain the invariant. Moreover, if a globally coordinated transaction leads
to another segment, the coordination ensures that all servers begin in the same
start state and with the same active segment, reestablishing the assumptions of
the \invariantconfluence{} system model.
